Jackson Strand

### 2024-03-09 index.qmd
update about me page picture

---
about: 
  template: jolla
  id: about-block
  image: "img/aboutme/crescent.HEIC"
  links:
    - icon: linkedin
      text: LinkedIn
      href: https://linkedin.com/in/jacksonstrand
    - icon: instagram
      text: Instagram
      href: https://www.instagram.com/jstrand894/
    - icon: github
      text: GitHub
      href: https://github.com/jstrand894 
---
::: {#about-block}
:::

>>>>

---
about: 
  template: jolla
  id: about-block
  image: "img/aboutme/crescent.jpg"
  links:
    - icon: linkedin
      text: LinkedIn
      href: https://linkedin.com/in/jacksonstrand
    - icon: instagram
      text: Instagram
      href: https://www.instagram.com/jstrand894/
    - icon: github
      text: GitHub
      href: https://github.com/jstrand894 
---
::: {#about-block}
:::
